%!TEX root=../main.tex
\documentclass[../main.tex]{subfiles}
\begin{document}
\subsection{David}
\begin{itemize}
    \item Learning the PyTorch framework. I have never worked with PyTorch before and it was a joy to learn. 
    \item Learning about GANs. Before this project i had no idea that GANs even existed. I think it's brilliant how it utilizes the min-max principle you often see in AI for games such as chess etc.
    \item Learning about feature space representations. I have delved into different approaches of how you can get something meaningful from words and explored bag of words models, word2vec and structured scene graphs. I have learned that the concept of context is not an easy one to transfer into machine learning algorithms.
\end{itemize}
\subsection{Qingyan}
\begin{itemize}
    \item Enjoying the process of team work and brain storming.
    \item Learning some text to image methods. This experience make me addicted to this field. I find another method called Image Generation from Scene Graphs presented by Justin Johnson. From the paper, this method can produce image with more complex relationship. I will try it in the summer holiday.
    \item Through the project, we learn how to complete a research, from idea finding, paper searching, coding to report writing. This will be really helpful for my master thesis and future work. 
\end{itemize}
\subsection{Sabeen}
\begin{itemize}
    \item I learned how to process speech data using Mel frequency cepstral coefficients. Prior to this project, I had no idea about how to extract features from audio files. 
    \item I also learned how to implement a k-layer network with batch normalization and training it using cyclic learning rate. 
    \item Learning about GANs was also very interesting.
    \item I also read up alot on RNNs with lstm cells because we were initially thinking of using those for speech recognition but we were not able to implement it successfully so we had to switch to a more simple network in a very late stage of the project. However, I did learn alot about RNNs. 
\end{itemize}
\end{document}